---
title: 'Statistical report: XXX'
subtitle: 'DRAFT'
author: 'Statistician: Lina Benson'
  
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    number_sections: yes
link-citations: yes
bibliography: references.bib
nocite: '@*'
urlcolor: blue
linkcolor: black
header-includes:
   - \usepackage{draftwatermark}
   - \usepackage{subfig}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
---

\newpage 
\tableofcontents 
\listoftables
\listoffigures
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, include = TRUE, comment = "",
  warning = FALSE, message = FALSE, fig.pos = "H",
  fig.path = "../output/figs/"
)
options(knitr.kable.NA = "")
```

```{r adjust_directory_if_needed, include=FALSE}
# Uncomment lines below if rmd file is placed in a subdirectory
knitr::opts_knit$set(root.dir = normalizePath("../"))
```

```{r load_project}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and code in lib directory

ProjectTemplate::reload.project()

cacheon <- TRUE
```             

# Data handling

## Data source

SHFDB3, https://kiheartfailure.github.io/shfdb3/, v 3.x.x. 

## Inclusion/exclusion criteria

```{r flow}
#default_kable(flow, caption = "Flowchart")
```

First patient in: `r min(rsdata$shf_indexdtm)` and last patient in: `r max(rsdata$shf_indexdtm)`.  

The median age (IQR) is `r rsdata %>% summarise(med = fn(median(shf_age), dig = 1),
                                             q1 = fn(quantile(shf_age, probs = 0.25), dig = 1),
                                             q3 = fn(quantile(shf_age, probs = 0.75), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", q1, "-", q3, ")")) %>%
                                   pull(out)` and 
`r rsdata %>% count(shf_sex) %>%
  mutate(perc = fn(n / sum(n) * 100, 1)) %>%
  filter(shf_sex == "Female") %>%
  pull(perc)`% females.    

## Created variables 

```{r npr}
#default_kable(metaout, caption = "Additional outcomes from NPR")
```

# Statistical analysis 

## General

All analyses were performed using `r sessionInfo()$R.version$version.string` [@r]. 
The level of significance is set to 5%, two-sided. No adjustment for multiple 
comparisons were made and therefore the results should be viewed with some care.

## Missing data

Missing data was imputed with multiple imputation (n = 10) using mice [@mice]. 
Variables included in the model are indicated in 
Table \ref{tab:tab1}. The primary outcome was included as the Nelson-Aalen estimator.

## Propensity scores and matching

A propensity score for treatment was estimated for each patient with 
logistic regression for each of the 10 imputed datasets using the variables 
indicated in Table \ref{tab:tab1}. 1:X matching without replacement [@match] 
was thereafter performed on the average of the resulting 10 ps [@psmatch]. Matching was 
allowed if the propensity score differed by 0.01 or less. The ability of the ps 
matching to balance the baseline characteristics was assessed by 
standardized mean differences.  

1:X has deemed the best option when taking into account the number of patients retained and balance between groups.
Other matching ratios: `r matchingn`.

## Baseline characteristics

```{r, child = "./src/tab1.Rmd"}

```

## Outcome analysis

The following outcomes are considered: 

Data were censored at 2019-12-31 or death/emigration. 

The outcomes are presented with the 1 - Kaplan-Meier curves with the overall p 
from the crude cox regression presented in the figure. Cox proportional hazards regressions were 
used to model the time to first event analysis and negative 
binomial regression including the log of time as an offset in the model for 
the repeated events. 

### Assumptions

The proportional hazards assumption was investigated using the scaled Schoenfeld 
residuals (cox.zph in [@survival-package]) for the primary outcome. 
Possible outliers were visually inspected by plotting the dfbetas. 
=> XXXX. 

The median (min-max) follow-up is 
`r rsdata %>% summarise(med = fn(median(sos_outtime_death / 365.25 * 12), dig = 1),
                                             min = fn(min(sos_outtime_death / 365.25 * 12), dig = 1),
                                             max = fn(max(sos_outtime_death / 365.25 * 12), dig = 1)) %>%
                                   mutate(out = paste0(med, " (", min, "-", max, ")")) %>%
                                   pull(out)` months for a total of 
                                   `r rsdata %>% summarise(sumpy = fn(sum(sos_outtime_death) / 365.25, dig = 0)) %>%
                                   pull(sumpy)` patient-years of follow-up.


```{r, child = "./src/km.Rmd"}

```

```{r, child = "./src/outtab.Rmd"}

```

\clearpage
\newpage

### Subgroups

Performed using an interaction term between XX and XX on the patients in the matched cohort. 
Note that there is missing data for XX so the matching (and thereby the adjustment) 
may therefore be incomplete. 

```{r, child = "./src/forest.Rmd"}

```

\clearpage
\newpage

# Reproducibility

## R session information {#sessioninfo}

```{r sessinfo}
sessionInfo()
```

## R code

The R code for all data handling and statistical analyses are found: 
https://github.com/KIHeartFailure/xx. On publication
the repository will be made public so as to 
link to it from the resulting article for increased transparency and code sharing.
No data or output is stored in the repository. 

# References